---
title: "Rmarkdown course - practical"
subtitle: "Overview and tasks"
format:
  pdf:
    number_sections: true
    toc: true
    include-in-header: header.tex
bibliography: Biblio_Example.bib
execute:
  echo: false
---

```{r}
#| label: setup
#| include: false

library(tidyverse)
library(pander)
library(kableExtra)
```

\newpage

# Intro

This document lists the available example-documents, provides tasks and serves as an example-rmarkdown-document in itself.

A good way to learn rmarkdown is to take a look at the pdf-version and try to recreate it.

# Overview material

 - The slides contain an overview, example-code and -output and **a lot of links to additional material**. If you can't find what you need in the slides or the provided links, check [stackoverflow](https://stackoverflow.com/questions/tagged/r-markdown)
 - An example of a latex header-file is header.tex (used for this document as well)
 - Formatting word output:
     - render *Ex_Word.qmd* with and without *reference_docx: WordTemplate.docx* in the YAML-header
 - Repeated section:
     - open, inspect and run *Ex_RepeatedSection1.qmd*
     - *Child_RepeatedSection1.qmd* is the 'child'-rmd that is repeated in the for loop
     - *Ex_RepeatedSection2.qmd* and *Child_RepeatedSection2.qmd* provide a slightly different example
 - Repeated report:
     - open, inspect an run *Ex_AutomatedReport_Main.R*
     - *Ex_AutomatedReport_Report.qmd* is the rmarkdown file that produces each seperate report

     
# Some examples

This sections presents some examples.


\blandscape

## A landscape page


```{r}

Nrow <- 6
Ncol <- 3

pander(mtcars[1:Nrow,1:Ncol], 
       caption = "A part of the cars data")

```


\elandscape

## A table, a graph and some inline-R-code


The table on the landscape page presented only `r Nrow` of the `r nrow(cars)` rows and only `r  Ncol` of the `r ncol(cars)` columns. Here is a fancy kableExtra version of the same table



```{r}

kable(mtcars[1:Nrow,1:Ncol]%>%
        arrange(cyl)%>%
        mutate(mpg = cell_spec(mpg, format = "latex", angle = ifelse(mpg > 21, 30, 0))), 
        booktabs = TRUE, linesep = "", escape = FALSE)%>%
  kable_styling(latex_options = "striped")
  

```


On the same page a graph:

```{r}
#| fig-height: 3
#| fig-width: 3
#| fig-cap: a nice mtcars-graph
#| fig-align: center

ggplot(mtcars, aes(hp, mpg, color = factor(cyl)))+
  geom_point()+
  theme_bw()

```

## A citation

Here is a citation from the example bibliography: [@ahnRandomizedTrialStents2015]




\newpage

# Tasks

(notice this starts on a new page)

  1. Open the Rmd-examples
     
     - check if you understand the code
     - run the markdown, check if it runs without errors
     
  2. Start from scratch:
  
     - Open a new rmarkdown
     - Adapt the yaml-header such that
        + there is a table of contents up to only 1 level (so excluding 3.1 or 3.1.a)
        + sections are numbered
     - Make a document with three sections:
        + Section 1:
           - a ggplot-graph with the mtcars-dataset, you can choose
           - exactly the same graph, but much bigger and right aligned
           - an external png
           - create a new subsection for each of the graphs
        + Section 2:
           - starts on a new page
           - Two subsections. In each of these subsections, recreate (starting from mtcars) one of the two tables on p. 14 of the [kableExtra vignette](https://cran.r-project.org/web/packages/kableExtra/vignettes/awesome_table_in_pdf.pdf)
       + Section 3:
          - Automate the production of a separate subsection for the set of cars with the same number of cylinders (variable cyl)
          - Each subsection contains a graph of hp vs mpg
      + Check with the solution. Play around with every parameter/piece of code you can find and check the result
    


\newpage

# Example-Bibliography